\documentclass[11pt]{article}
\topmargin-2.0cm
\usepackage[colorlinks,citecolor=blue]{hyperref}
\usepackage[dvips]{color}
\usepackage[square,numbers]{natbib}
\usepackage{graphicx} 
\usepackage{amssymb}
\newcommand{\vect}[1]{\boldsymbol{\mathbf{#1}}}
\advance\oddsidemargin-0.75in
\textheight9in
\textwidth6.5in
\newcommand\bb[1]{\mbox{\em #1}}
\def\baselinestretch{1.05}

\newcommand{\hsp}{\hspace*{\parindent}}
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\renewcommand\bibname{References}

%\usepackage{fancyhdr}
%\pagestyle{fancy} 
%\usepackage{datetime}
\definecolor{gray}{rgb}{0.4,0.4,0.4}

% declarations for front matter
\usepackage{xspace}
\usepackage{subfigure}
\usepackage{url}
\newcommand{\autotuning}{autotuning\xspace}
\newcommand{\R}{\mathbb{R}} % For the reals
\newcommand{\cD}{\mathcal{D}} % For a domain
\newcommand{\cC}{\mathcal{C}} % For a discrete domain set
\newcommand{\cI}{\mathcal{I}} % For an integer domain set
%\newcommand{\cB}{\mathcal{B}} % For a binary domain set
\newcommand{\cR}{\mathcal{R}} % For a binary domain set
\newcommand{\Note}{\marginpar[\textbf{$\Longrightarrow$}]{\textbf{$\Longleftarrow$}}} % For margin notes
%\newcommand{\Ref}[1]{Eq.~\mbox{\rm{(\ref{#1})}}}    % References with ()
\newcommand{\UJ}{\textsf{\small UJ}} % For unroll jam transformation
\newcommand{\SR}{\textsf{\small SR}} % For scalar replacement transformation
\newcommand{\LP}{\textsf{\small LP}} % For loop parallelization transformation
\newcommand{\LV}{\textsf{\small LV}} % For loop vectorization transformation
\newcommand{\RT}{\textsf{\small RT}} % For register tiling transformation



\newcommand{\cX}{\mathbf{X}}   % decision space
\newcommand{\cF}{\mathbf{F}}   % objective space
\newcommand{\eps}{\varepsilon}

\usepackage{amsopn,amsmath}
\DeclareMathOperator{\minimize}{minimize}
\setlength{\bibsep}{0pt plus 0.3ex}
\usepackage{xcolor}
\newcommand{\PB}[1]{\textcolor{red}{PB: #1}}
\usepackage{comment}

\begin{document}
\pagestyle{empty}

\subsection*{Biographical sketch for Dr.~Romit Maulik}

\begin{tabbing}
  \=Leadership Computing Facility,\\
  \>Argonne National Laboratory, 
Lemont, IL 60439\\
  \>Phone:  (405) 982-0161; Email:  \href{mailto:rmaulik@anl.gov}{\bf \texttt{rmaulik@anl.gov}}
\end{tabbing}


\subsection*{Education and Training}
% Undergraduate, graduate and postdoctoral training, provide
% institution, major/area, degree and year ...
\noindent	Argonne National Laboratory, Leadership Computing Facility, Postdoc, 2019--Present.\\
	Oklahoma State University, Mechanical \& Aerospace Engineering, Ph.D., 2019.\\
	Oklahoma State University, Mechanical \& Aerospace Engineering, M.S., 2015.\\
	Birla Institute of Technology, India, Mechanical Engineering, Bachelor of Engineering, 2012.


\subsection*{Research and Professional Experience}
% Beginning with the current position list, in chronological order,
% professional/academic positions with a brief description.
\noindent 2019--Present: {\em Postdoctoral Fellow}, Leadership Computing Facility, Argonne National Laboratory.\\
2019--2019: {\em Predoctoral Fellow}, Mathematics \& Computer Science division, Argonne National Laboratory.\\ 
2014--2018: {\em Graduate Research Assistant}, Mechanical \& Aerospace Engineering, Oklahoma State University.\\ 
2012--2013: {\em Design Engineer}, Tata Technologies Ltd., Pune, India.


\subsection*{Honors and Awards}
\noindent {\bf[1]} Margaret Butler Fellowship, Leadership Computing Facility, 2019. \\
{\bf[2]} Outstanding Graduate Student, College of Engineering Architecture and Technology, Oklahoma State University, 2018. \\
{\bf[3]} Graduate College Robberson Summer Research Fellowship, Oklahoma State University, 2017. \\
{\bf[4]} John Brammer Fellowship, Oklahoma State University, 2016. \\
{\bf[5]} Graduate College Top Tier Fellowship, Oklahoma State University, 2016.

\subsection*{Related Publications}
\begin{enumerate}
\parskip = -2pt

\item S. Renganathan \textbf{R. Maulik}, V. Rao : Machine learning for Nonintrusive Model Order Reduction of the Parametric Inviscid Transonic Flow past an airfoil, {\it Accepted in-press, Physics of Fluids}, 2020.

\item \textbf{R. Maulik}, O. San, J. Jacob: Spatiotemporally dynamic implicit large eddy simulation using machine learning classifiers, {\it Physica D.}, 406, 132409, 2020.

\item \textbf{R. Maulik}, A. Mohan, B. Lusch, S. Madireddy, P. Balaprakash, D. Livescu: Time-series learning of latent-space dynamics for reduced-order model closure, {\it Physica D.}, 405, 132368, 2020.

\item \textbf{R. Maulik}, V.Rao, S. Madireddy, B. Lusch, P. Balaprakash: Using recurrent neural networks for nonlinear component computation in advection-dominated reduced-order models, \textit{Machine learning for Physical Sciences workshop, NeurIPS}, 2019.

\item \textbf{R. Maulik}, O. San, J. Jacob, C. Crick: Online turbulence model classification for large eddy simulation using deep learning, {\it Journal of Fluid Mechanics}, 870, 784-812, 2019.

\item \textbf{R. Maulik}, O. San, A. Rasheed, P. Vedula: Subgrid modeling for two-dimensional turbulence using artificial neural networks, {\it Journal of Fluid Mechanics}, 858, 122-144, 2019.

\item \textbf{R. Maulik}, O. San, A. Rasheed, P. Vedula: Data-driven deconvolution for large eddy simulation of Kraichnan turbulence, {\it Physics of Fluids}, 30, 125109, 2018.

\item O.San, \textbf{R.Maulik}: Extreme learning machine for reduced order modeling of turbulent geophysical flows, {\it Physical Review E}, 97, 042322, 2018.

\item O.San, \textbf{R.Maulik}: Machine learning closures for model order reduction of thermal fluids,  {\it Applied Mathematical Modelling}, https://doi.org/10.1016/j.apm.2018.03.037, 2018.

\item \textbf{R.Maulik}, O.San: A neural network approach for the blind deconvolution of turbulent flows, {\it Journal of Fluid Mechanics}, 831, 151-181, 2017.

\end{enumerate}

\subsection*{Synergistic Activities}
\begin{enumerate}
\parskip = -2pt
%
\item Program Committee - Argonne Data Science Project allocations : Reviewed allocation requests for 21 million core hours and 190 TB storage.
\item Co-organizer - Argonne National Laboratory - AI, Statistics and Machine Learning Journal Club.
\item Session chair - AIAA Aviation Forum, Reno, NV, 2020.
\item Session chair - SIAM Conference on Mathematics of Data Science, Cincinnati, OH, 2020.
\item Session chair - SIAM Conference on Computational Science and Engineering, Spokane, WA, 2019.
\end{enumerate}

\end{document}

